How has the Brazilian Amazon been constructed as a problem? The economy, the environment, the people, and the nation in the presidential speeches since 1985

### 2022-08-23 Draft_June_2022/Full_draft_20220608.rmd
Updated code chunk names (should avoid multple words) and plots for in and out the amazon (figure 2)

perc_in <- pop %>%
   mutate(location_cat = ifelse(grepl("International|Non Identified", location_cat),
                                "Outside of Brazil", "In Brazil")) %>%
   count(amazon_speech, year, location_cat) %>%
   group_by(year) %>%
   mutate(perc = n / sum(n)) %>%
   filter(amazon_speech == 1) %>%
   select(c(perc, amazon_speech, year, location_cat))

@@

# location plots

Amazon_year_in <- perc_in %>% filter(location_cat== "In Brazil") %>% 
  ggplot(., aes(x = year, y = perc))+
  geom_line(color="darkgreen")+
  geom_line(aes(y=mean(perc)), color="black", size=.5)+
  geom_vline(xintercept = c(1988.9, 1992, 2009, 2015, 2019), linetype = "dotted")+
  scale_y_continuous(labels = percent_format())+
  labs(x = "", y = "",
       subtitle = "Speeches in Brazil (n=4416)",
       color='Y series') +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "bold"),
        legend.position = "")

Amazon_year_out <- perc_in %>% filter(location_cat== "Outside of Brazil") %>% 
  ggplot(., aes(x = year, y = perc))+
  geom_line(color="darkgreen")+
  geom_line(aes(y=mean(perc)), color="black", size=.5)+
  geom_vline(xintercept = c(1988.9, 1992, 2009, 2015, 2019), linetype = "dotted")+
  scale_y_continuous(labels = percent_format())+
  labs(x = "", y = "",
       subtitle = "Speeches outside of Brazil (n=1714)",
       caption= "Black lines portray the means.",
       color='Y series') +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "bold"),
        legend.position = "")

@@

```{r comparison with inequality, crime, and inflation eval=FALSE, include=FALSE}

# # comparison with inequality, crime and inflation in speeches
# pop <- pop %>%
#   mutate(desigual = ifelse(grepl("desigual", text, ignore.case = TRUE), 1, 0),
#          crime = ifelse(grepl("violencia|crime|criminalidade|seguranca publica",
#                               text, ignore.case = TRUE), 1, 0),
#          inf = ifelse(grepl("inflacao|inflaçao",
#                              text, ignore.case = TRUE), 1, 0),
#          unemploy = ifelse(grepl("desempreg",
#                              text, ignore.case = TRUE), 1, 0))
# perc2 <- pop %>%
#   count(desigual, year) %>%
#   group_by(year) %>%
#   mutate(perc=n / sum(n)) %>%
#   filter(desigual == 1) %>%
#   select(c(perc, desigual, year))
# perc3 <- pop %>%
#   count(crime, year) %>%
#   group_by(year) %>%
#   mutate(perc=n / sum(n)) %>%
#   filter(crime == 1) %>%
#   select(c(perc, crime, year))
# perc4 <- pop %>%
#   count(inf, year) %>%
#   group_by(year) %>%
#   mutate(perc=n / sum(n)) %>%
#   filter(inf == 1) %>%
#   select(c(perc, inf, year))
# perc5 <- pop %>%
#   count(unemploy, year) %>%
#   group_by(year) %>%
#   mutate(perc=n / sum(n)) %>%
#   filter(unemploy == 1) %>%
#   select(c(perc, unemploy, year))
# colors <- c("Amazon Speech" = "green", "Inequality Speech" = "red",
#             "Criminality Speech" = "yellow", "Inflation Speech" = "blue",
#             "Unemployment Speech" = "purple")
# Amazon_vs_other <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
#   geom_line(aes(color = "Amazon Speech")) +
#   geom_line(data = perc2, aes(x = year, y = perc, color = "Inequality Speech")) +
#   geom_line(data = perc3, aes(x = year, y = perc, color = "Criminality Speech")) +
#   geom_line(data = perc4, aes(x = year, y = perc, color = "Inflation Speech")) +
#   geom_line(data = perc5, aes(x = year, y = perc, color = "Unemployment Speech")) +
#   scale_y_continuous(labels = percent_format()) +
#   scale_color_manual(values = colors) +
#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon in by year",
#        subtitle = "Sample composed by 6130 presidential speeches since 1985 and compared with mentions of other salient policy objects across the same speeches",
#        caption = "",
#        color = "Legend\n") +
#   theme(panel.background = element_rect("white", "black", .5, "solid"),
#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
#         axis.text = element_text(color = "black", size = 10),
#         title = element_text(color = "black", size = 10, face = "bold"),
#         legend.title = element_blank(),
#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
#         legend.position = "bottom")
# Amazon_vs_other
# Amazon_vs_other_mean <- tibble::tibble("Policy Object" = c("Amazon", "Inequality",
#                                                            "Criminality", "Inflation",
#                                                            "Unemployment"),
#                                        "Mean share in time" = c(mean(perc1$perc),
#                                                                 mean(perc2$perc),
#                                                                 mean(perc3$perc),
#                                                                 mean(perc4$perc),
#                                                                 mean(perc5$perc)))
# Amazon_vs_other_mean

# comparison with inequality, crime and inflation in speeches
# pop <- pop %>%
#   mutate(desigual = ifelse(grepl("desigual", text, ignore.case = TRUE), 1, 0),
#          crime = ifelse(grepl("violencia|crime|criminalidade|seguranca publica",
#                               text, ignore.case = TRUE), 1, 0),
#          inf = ifelse(grepl("inflacao|inflaçao",
#                              text, ignore.case = TRUE), 1, 0),
#          unemploy = ifelse(grepl("desempreg",
#                              text, ignore.case = TRUE), 1, 0))
# perc2 <- pop %>%
#   count(desigual, year) %>%
#   group_by(year) %>%
#   mutate(perc=n / sum(n)) %>%
#   filter(desigual == 1) %>%
#   select(c(perc, desigual, year))
# perc3 <- pop %>%
#   count(crime, year) %>%
#   group_by(year) %>%
#   mutate(perc=n / sum(n)) %>%
#   filter(crime == 1) %>%
#   select(c(perc, crime, year))
# perc4 <- pop %>%
#   count(inf, year) %>%
#   group_by(year) %>%
#   mutate(perc=n / sum(n)) %>%
#   filter(inf == 1) %>%
#   select(c(perc, inf, year))
# perc5 <- pop %>%
#   count(unemploy, year) %>%
#   group_by(year) %>%
#   mutate(perc=n / sum(n)) %>%
#   filter(unemploy == 1) %>%
#   select(c(perc, unemploy, year))
# colors <- c("Amazon Speech" = "green", "Inequality Speech" = "red",
#             "Criminality Speech" = "yellow", "Inflation Speech" = "blue",
#             "Unemployment Speech" = "purple")
# Amazon_vs_other <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
#   geom_line(aes(color = "Amazon Speech")) +
#   geom_line(data = perc2, aes(x = year, y = perc, color = "Inequality Speech")) +
#   geom_line(data = perc3, aes(x = year, y = perc, color = "Criminality Speech")) +
#   geom_line(data = perc4, aes(x = year, y = perc, color = "Inflation Speech")) +
#   geom_line(data = perc5, aes(x = year, y = perc, color = "Unemployment Speech")) +
#   scale_y_continuous(labels = percent_format()) +
#   scale_color_manual(values = colors) +
#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon in by year",
#        subtitle = "Sample composed by 6130 presidential speeches since 1985 and compared with mentions of other salient policy objects across the same speeches",
#        caption = "",
#        color = "Legend\n") +
#   theme(panel.background = element_rect("white", "black", .5, "solid"),
#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
#         axis.text = element_text(color = "black", size = 10),
#         title = element_text(color = "black", size = 10, face = "bold"),
#         legend.title = element_blank(),
#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
#         legend.position = "bottom")
# Amazon_vs_other
# Amazon_vs_other_mean <- tibble::tibble("Policy Object" = c("Amazon", "Inequality",
#                                                            "Criminality", "Inflation",
#                                                            "Unemployment"),
#                                        "Mean share in time" = c(mean(perc1$perc),
#                                                                 mean(perc2$perc),
#                                                                 mean(perc3$perc),
#                                                                 mean(perc4$perc),
#                                                                 mean(perc5$perc)))
# Amazon_vs_other_mean

@@

```{r Plot all regressions eval=FALSE, include=FALSE}

>>>>

perc_in <- pop %>%
   mutate(location_cat = ifelse(grepl("International|Non Identified",
                                      location_cat),
                                "Outside of Brazil", "In Brazil")) %>%
  filter(location_cat == "In Brazil") %>% 
  count(amazon_speech, year, location_cat) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>%
  filter(amazon_speech == 1) %>%
  select(c(perc, amazon_speech, year, location_cat))

perc_out <- pop %>%
   mutate(location_cat = ifelse(grepl("International|Non Identified",
                                      location_cat),
                                "Outside of Brazil", "In Brazil")) %>%
  filter(location_cat == "Outside of Brazil") %>% 
  count(amazon_speech, year, location_cat) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>%
  filter(amazon_speech == 1) %>%
  select(c(perc, amazon_speech, year, location_cat))

@@

# location plots
Amazon_year_in <- perc_in %>%
  ggplot(., aes(x = year, y = perc))+
  geom_line(color="darkgreen")+
  geom_line(aes(y=mean(perc)), color="black", size=.5)+
  geom_vline(xintercept = c(1988.9, 1992, 2009, 2015, 2019), linetype = "dotted")+
  scale_y_continuous(labels = percent_format())+
  labs(x = "", y = "",
       subtitle = "Speeches in Brazil (n=4344)",
       color='Y series') +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "bold"),
        legend.position = "")

Amazon_year_out <- perc_out %>% 
  ggplot(., aes(x = year, y = perc))+
  geom_line(color="darkgreen")+
  geom_line(aes(y=mean(perc)), color="black", size=.5)+
  geom_vline(xintercept = c(1988.9, 1992, 2009, 2015, 2019), linetype = "dotted")+
  scale_y_continuous(labels = percent_format())+
  labs(x = "", y = "",
       subtitle = "Speeches outside of Brazil (n=1786)",
       caption= "Black lines portray the means.",
       color='Y series') +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "bold"),
        legend.position = "")

@@

```{r comparison, eval=FALSE, include=FALSE}

# # comparison with inequality, crime and inflation in speeches
# pop <- pop %>%
#   mutate(desigual = ifelse(grepl("desigual", text, ignore.case = TRUE), 1, 0),
#          crime = ifelse(grepl("violencia|crime|criminalidade|seguranca publica",
#                               text, ignore.case = TRUE), 1, 0),
#          inf = ifelse(grepl("inflacao|inflaçao",
#                              text, ignore.case = TRUE), 1, 0),
#          unemploy = ifelse(grepl("desempreg",
#                              text, ignore.case = TRUE), 1, 0))
# perc2 <- pop %>%
#   count(desigual, year) %>%
#   group_by(year) %>%
#   mutate(perc=n / sum(n)) %>%
#   filter(desigual == 1) %>%
#   select(c(perc, desigual, year))
# perc3 <- pop %>%
#   count(crime, year) %>%
#   group_by(year) %>%
#   mutate(perc=n / sum(n)) %>%
#   filter(crime == 1) %>%
#   select(c(perc, crime, year))
# perc4 <- pop %>%
#   count(inf, year) %>%
#   group_by(year) %>%
#   mutate(perc=n / sum(n)) %>%
#   filter(inf == 1) %>%
#   select(c(perc, inf, year))
# perc5 <- pop %>%
#   count(unemploy, year) %>%
#   group_by(year) %>%
#   mutate(perc=n / sum(n)) %>%
#   filter(unemploy == 1) %>%
#   select(c(perc, unemploy, year))
# colors <- c("Amazon Speech" = "green", "Inequality Speech" = "red",
#             "Criminality Speech" = "yellow", "Inflation Speech" = "blue",
#             "Unemployment Speech" = "purple")
# Amazon_vs_other <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
#   geom_line(aes(color = "Amazon Speech")) +
#   geom_line(data = perc2, aes(x = year, y = perc, color = "Inequality Speech")) +
#   geom_line(data = perc3, aes(x = year, y = perc, color = "Criminality Speech")) +
#   geom_line(data = perc4, aes(x = year, y = perc, color = "Inflation Speech")) +
#   geom_line(data = perc5, aes(x = year, y = perc, color = "Unemployment Speech")) +
#   scale_y_continuous(labels = percent_format()) +
#   scale_color_manual(values = colors) +
#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon in by year",
#        subtitle = "Sample composed by 6130 presidential speeches since 1985 and compared with mentions of other salient policy objects across the same speeches",
#        caption = "",
#        color = "Legend\n") +
#   theme(panel.background = element_rect("white", "black", .5, "solid"),
#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
#         axis.text = element_text(color = "black", size = 10),
#         title = element_text(color = "black", size = 10, face = "bold"),
#         legend.title = element_blank(),
#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
#         legend.position = "bottom")
# Amazon_vs_other
# Amazon_vs_other_mean <- tibble::tibble("Policy Object" = c("Amazon", "Inequality",
#                                                            "Criminality", "Inflation",
#                                                            "Unemployment"),
#                                        "Mean share in time" = c(mean(perc1$perc),
#                                                                 mean(perc2$perc),
#                                                                 mean(perc3$perc),
#                                                                 mean(perc4$perc),
#                                                                 mean(perc5$perc)))
# Amazon_vs_other_mean
# #comparison with inequality, crime and inflation in speeches
# pop <- pop %>%
#   mutate(desigual = ifelse(grepl("desigual", text, ignore.case = TRUE), 1, 0),
#          crime = ifelse(grepl("violencia|crime|criminalidade|seguranca publica",
#                               text, ignore.case = TRUE), 1, 0),
#          inf = ifelse(grepl("inflacao|inflaçao",
#                              text, ignore.case = TRUE), 1, 0),
#          unemploy = ifelse(grepl("desempreg",
#                              text, ignore.case = TRUE), 1, 0))
# perc2 <- pop %>%
#   count(desigual, year) %>%
#   group_by(year) %>%
#   mutate(perc=n / sum(n)) %>%
#   filter(desigual == 1) %>%
#   select(c(perc, desigual, year))
# perc3 <- pop %>%
#   count(crime, year) %>%
#   group_by(year) %>%
#   mutate(perc=n / sum(n)) %>%
#   filter(crime == 1) %>%
#   select(c(perc, crime, year))
# perc4 <- pop %>%
#   count(inf, year) %>%
#   group_by(year) %>%
#   mutate(perc=n / sum(n)) %>%
#   filter(inf == 1) %>%
#   select(c(perc, inf, year))
# perc5 <- pop %>%
#   count(unemploy, year) %>%
#   group_by(year) %>%
#   mutate(perc=n / sum(n)) %>%
#   filter(unemploy == 1) %>%
#   select(c(perc, unemploy, year))
# colors <- c("Amazon Speech" = "green", "Inequality Speech" = "red",
#             "Criminality Speech" = "yellow", "Inflation Speech" = "blue",
#             "Unemployment Speech" = "purple")
# Amazon_vs_other <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
#   geom_line(aes(color = "Amazon Speech")) +
#   geom_line(data = perc2, aes(x = year, y = perc, color = "Inequality Speech")) +
#   geom_line(data = perc3, aes(x = year, y = perc, color = "Criminality Speech")) +
#   geom_line(data = perc4, aes(x = year, y = perc, color = "Inflation Speech")) +
#   geom_line(data = perc5, aes(x = year, y = perc, color = "Unemployment Speech")) +
#   scale_y_continuous(labels = percent_format()) +
#   scale_color_manual(values = colors) +
#   labs(x = "", y = "", title ="Share of speeches mentioning the Amazon in by year",
#        subtitle = "Sample composed by 6130 presidential speeches since 1985 and compared with mentions of other salient policy objects across the same speeches",
#        caption = "",
#        color = "Legend\n") +
#   theme(panel.background = element_rect("white", "black", .5, "solid"),
#         panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
#         axis.text = element_text(color = "black", size = 10),
#         title = element_text(color = "black", size = 10, face = "bold"),
#         legend.title = element_blank(),
#         plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
#         legend.position = "bottom")
# Amazon_vs_other
# Amazon_vs_other_mean <- tibble::tibble("Policy Object" = c("Amazon", "Inequality",
#                                                            "Criminality", "Inflation",
#                                                            "Unemployment"),
#                                        "Mean share in time" = c(mean(perc1$perc),
#                                                                 mean(perc2$perc),
#                                                                 mean(perc3$perc),
#                                                                 mean(perc4$perc),
#                                                                 mean(perc5$perc)))
# Amazon_vs_other_mean

@@

```{r regressions, eval=FALSE, include=FALSE}
